\section{Generative Reactor Design}
For nuclear reactors, generative design is constrained by 
variables such as mass or volume of fuel, fuel enrichment, effectiveness 
of heat transfer, effective neutron multiplication factor, etc. 
Nuclear reactors not only experience physical forces, but also
require evaluation of the neutronics of the system, therefore generative design of 
a nuclear reactor cannot make use of tools such as Autodesk Fusion360 or SolidWorks 
Topology. 
Therefore, a framework that couples well-developed advanced genetic algorithms 
with well-supported monte-carlo particle transport 
codes (Serpent \cite{leppanen_serpent_2014}, 
MCNP \cite{werner_mcnp6._2018}, etc.) and thermal hydraulics 
codes (RELAP7 \cite{andrs_relap-7_2012} etc.)
must be created to successfully produce generative reactor designs. 

Cacuci \cite{cacuci_global_1990} has previously applied global optimization 
to the field of nuclear reactor design. 
Genetic algorithms have also been successfully applied to nuclear core reload optimization
\cite{dechaine_nuclear_1995,chapot_new_1999,schirru_genetic_1997,feltus_incorporating_1997}, 
transient classification \cite{alvarenga_adaptive_1997, mol_neural_2006}, 
core designs \cite{pereira_basic_1999,kumar_new_2015}, 
\gls{SNF} solvent extraction process 
\cite{omori_applications_1997}, design of a Fast Neutron Source (FNS) 
\cite{pevey_genetic_2019}, and finding optimized cutting paths for nuclear 
reactor decommissioning \cite{tsai_computer_2019}.  
Kumar et al \cite{kumar_new_2015} used genetic algorithms with reduced order models 
of neutronics and thermal hydraulics of the reactor to predict output parameters 
for the inputs generated by the genetic algorithm, resulting in reduced computational 
cost. 

All applications using genetic algorithms for reactor core optimization 
have varied the parameters in classical reactor geometries such as radius of 
fuel pellet and clad, enrichment of fuel, pin pitch, etc. 
Therefore, choosing parametric genetic algorithms over cell algorithms. 
In recent years, additive manufacturing technology has advanced and has altered 
the way in which components are designed and manufactured 
\cite{simpson_considerations_2019}. 
Key additive manufacturing technologies relevant to nuclear reactor 
core structures are \gls{SLM}, \gls{EBM}, and \gls{L-DED}.
The \gls{SLM} and \gls{EBM} techniques have been used for 
automotive and aircraft component fabrication \cite{murr_frontiers_2016}. 
Successful examples of additive manufacturing applied in the the aircraft industry
are Boeing's use of additive manufacturing to reduce weight in the 787 Dreamliner
\cite{noauthor_printed_2017} and SES-15 spacecraft \cite{noauthor_boeing_nodate}. 
Using additive manufacturing to fabricate nuclear reactor components will 
drastically reduce cost, timelines, increase safety and performance by tailoring 
local material properties and redesigning geometries for optimal load paths 
\cite{simpson_considerations_2019}. 
With further advancement of these additive manufacturing technologies, 
a reactor core could be 3D printed in the near future. 
Therefore, with the capability to 3D print a nuclear reactor, genetic algorithms 
can be leveraged to optimize the reactor core in non-classical ways, such as wavy
coolant channels and spatially-variant optimized packing of \gls{TRISO} particles, 
etc.  
% cite pre application narrative? 


\subsection{Workflow}
% How the genetic algorithm is coupled with a CAD designer and analysis tool 
% (serpent/RELAP)
% CAD designer > grasshopper3d (see Bryne Paper)
Figure \ref{fig:workflow} depicts a framework for leveraging genetic algorithms
to design nuclear reactors. 
This is a general framework that does not specify algorithms or analytical 
softwares. 
Instead, it provides placeholders for algorithm and software types, so 
that a user may choose the types of algorithms and softwares they want to use in 
their mission towards using generative design to design a nuclear reactor. 
Table \ref{tab:examples} lists algorithm and software types that could be used 
in the framework. 

\begin{figure}[!htbp]
        \centering
        \begin{tikzpicture}[node distance=2cm]
                \tikzstyle{every node}=[font=\small]
                \node[anchor=west] (1) [noblock] {\textbf{Create}};
                \node (2) [bblock, right=of 1] {\textbf{GA: Creates population}};
                \node (3) [pblock, right=of 2] {\textbf{GGS: Generates reactor designs}};
                \node[anchor=west] (4) [noblock, below of= 1] {\textbf{Analyze}};
                \node (5) [oblock, below of =2]{\textbf{NT: Run NT code for each solution}};
                \node (6) [gblock, right=of 5]{\textbf{TH: Run TH code for each solution}};
                \node[anchor=west] (7) [noblock, below of= 4] {\textbf{Evaluate}};
                \node (8) [bblock, below of =5] {\textbf{GA: Evaluate population}};
                \node (9) [ppblock, right=of 8] {\textbf{M: Evaluation based on performance metrics}};
                \node[anchor=west] (10) [noblock, below of= 7] {\textbf{Check}};
                \node (11) [lppblock, below of=8, xshift=3cm, yshift=-0.2cm] {\textbf{M: Is termination criteria met?}};
                \node (16) [lbblock, below of = 11] {\textbf{GA: Best solution is returned!}};
                \node[anchor=west] (12) [snoblock, above of= 2, xshift=3cm, yshift=-1.1cm] {};
                \node[anchor=west] (13) [snoblock, below of=12,yshift=-0.15cm] {};
                \node[anchor=west] (14) [snoblock, below of=13,yshift=-0.02cm] {};
                \node[anchor=west] (15) [snoblock, below of=14,yshift=-0.02cm] {};
                \node[anchor=west] (17) [noblock, below of= 10] {\textbf{Completed}};
                \draw [-,thick] (11) -- ([shift={(3cm,0cm)}]11.east) |- node[anchor=west, yshift=-4.2cm] {no} ([shift={(0cm,0.7cm)}]12.north)--(12);
                \draw [arrow] (12) -- ([shift={(0cm,0cm)}]12.north) |- ([shift={(0cm,0.4cm)}]2.north)--(2);
                \draw [arrow] (12) -- ([shift={(0cm,0cm)}]12.north) |- ([shift={(0cm,0.4cm)}]3.north)--(3);
                \draw [-,thick] (2) -- ([shift={(0cm,0cm)}]2.south) |- ([shift={(0cm,0.3cm)}]13.north)--(13);
                \draw [-,thick] (3) -- ([shift={(0cm,0cm)}]3.south) |- ([shift={(0cm,0.3cm)}]13.north)--(13);
                \draw [arrow] (13) -- ([shift={(0cm,0cm)}]13.north) |- ([shift={(0cm,0.3cm)}]5.north)--(5);
                \draw [arrow] (13) -- ([shift={(0cm,0cm)}]13.north) |- ([shift={(0cm,0.3cm)}]6.north)--(6);
                \draw [-,thick] (5) -- ([shift={(0cm,0cm)}]5.south) |- ([shift={(0cm,0.3cm)}]14.north)--(14);
                \draw [-,thick] (6) -- ([shift={(0cm,0cm)}]6.south) |- ([shift={(0cm,0.3cm)}]14.north)--(14);
                \draw [arrow] (14) -- ([shift={(0cm,0cm)}]14.north) |- ([shift={(0cm,0.3cm)}]8.north)--(8);
                \draw [arrow] (14) -- ([shift={(0cm,0cm)}]14.north) |- ([shift={(0cm,0.21cm)}]9.north)--(9);
                \draw [-,thick] (8) -- ([shift={(0cm,0cm)}]8.south) |- ([shift={(0cm,0.3cm)}]15.north)--(15);
                \draw [-,thick] (9) -- ([shift={(0cm,0cm)}]9.south) |- ([shift={(0cm,0.3cm)}]15.north)--(15);
                \draw [arrow] (15) -- ([shift={(0cm,0cm)}]15.north) |- ([shift={(0cm,0.1cm)}]11.north)--(11);
                \draw [arrow] (11) -- ([shift={(0cm,0cm)}]11.south) |- node[anchor=west, yshift=0.3cm] {yes} ([shift={(0cm,0.1cm)}]16.north)--(16);
                \matrix [draw,below left,yshift=-0.5cm, xshift=-7cm] at (current bounding box.south east) {
                \node [bbblock,label=right:\textbf{GA: Genetic algorithm}] {}; \\
                \node [bpblock,label=right:\textbf{GGS: Geometry generating software}] {}; \\
                \node [boblock,label=right:\textbf{NT: Neutron transport code}] {}; \\
                \node [bgblock,label=right:\textbf{TH: Thermal hydaulics code}] {}; \\
                \node [bppblock,label=right:\textbf{M: User-defined metrics/criteria}] {}; \\
                };
        \end{tikzpicture}
        \caption{Generative reactor design framework. Each component of the 
        framework is user-selected.}
        \label{fig:workflow}
\end{figure}

\begin{table}[!htbp]
        \caption{Example algorithm and software types to populate generative reactor 
        design framework (Fig \ref{fig:workflow}).}
        \label{tab:examples}
        \centering
        \doublespacing
        \small
        \begin{tabular}{lp{10cm}}
        \hline
        \textbf{Framework Component} & \textbf{Examples}\\ \hline
        Genetic algorithm driver & DEAP \cite{fortin_deap_2012} \\
        Geometry generating software & Trelis \cite{noauthor_trelis_2018}, FreeCAD \cite{falck_freecad_2012}, SolidWorks \cite{lombard_solidworks_2008}, grasshopper3d \cite{rutten_grasshopper3d_2015}, GenerativeComponents \cite{aish_bentleys_2003}, Trilinos \cite{heroux_overview_2003}, DAGMC \cite{smith_enhanced_2011} \\
        Neutron transport code & Serpent \cite{leppanen_serpent_2014}, MCNP \cite{werner_mcnp6._2018}, SCALE \cite{bucholz_scale:_1982}, OpenMC \cite{romano_openmc_2013} \\ 
        Thermal hydraulics code & RELAP5-3D \cite{strydom_comparison_2016}, RELAP7 \cite{andrs_relap-7_2012}, TRACE \cite{xu_multi-physics_2006}\\
        User-defined metrics/criteria & keff, heat transfer rate, fuel enrichment, mass of fuel \\ \hline
\end{tabular}
\end{table}

\subsection{Software}
The generative reactor design framework proposed (Fig. \ref{fig:workflow}) 
has many coupled components. 
To minimize the amount of coupling required, software is chosen with 
framework-leanness in mind. 
The shortlisted software will be evaluated based on the clearly 
defined requirements of each component. 
Each iteration of the framework requires the neutron transport code, 
the thermal hydraulics code, and evaluation to be run for each 
nuclear reactor geometry (individual) generated by the genetic algorithm, 
resulting in a high computational cost. 
Since each individual can be evaluated independently from others, 
individual runs must be parallelized to reduce computation time 
\cite{pereira_genetic_2000}. 
The generative reactor design framework is computation-heavy. 
To produce results in a timely manner, a supercomputer 
such as Blue Waters \cite{ncsa_about_2017} will be used. 
In summary, each component's software is chosen based on these 
conditions: 
\begin{enumerate}
    \item It best meets the clearly defined requirements 
    its respective component. 
    \item It is parallelizable. 
    \item It is compatible with a high performance computer. 
    \item It is open-source and free (preferable but not required). 
\end{enumerate}

The subsequent subsections will define the requirements of each 
component in the generative reactor framework, the software considered, 
and an explanation justifying the final software choice. 

\subsubsection{Genetic Algorithm Driver}
Evolutionary algorithm computation is a sophisticated field with diverse
techniques and mechanisms, resulting in even well designed frameworks 
being complicated under the hood \cite{fortin_deap_2012}. 
These implementation intricacies are difficult to extend since it requires 
the user to edit the source code. 
This is concerning since using evolutionary algorithms to solve unique 
real-world problems requires customization of algorithms 
\cite{fortin_deap_2012}. 
Therefore, an evolutionary algorithm computation framework that gives 
the user the capability to build custom evolutionary algorithms is 
required for this project. 

There are many evolutionary algorithm computation packages 
available: \gls{DEAP} \cite{fortin_deap_2012}, 
inspyred \cite{garrett_inspyred_2014}, 
Pyevolve \cite{perone_pyevolve_2009}, and
OpenBEAGLE \cite{gagne_open_2002}. 
DEAP is the most newly created package and places a high value on 
code compactness and code clarity \cite{fortin_deap_2012}. 
\gls{DEAP} is the only framework that allows the user to rapidly 
prototype evolutionary algorithms and define custom algorithms without 
having to dig deep into the source code to modify lines, making it 
the code of choice for the genetic algorithm driver component of 
the generative reactor design framework. 
\gls{DEAP} provides building blocks for each optimizer function and 
allows the user to customize and design a specialized algorithm 
to fit their project. 

\subsubsection{Geometry Generating Software}
The geometry generating software is the `filling' in the sandwich in which 
the top bun is the genetic algorithm driver and bottom bun is the 
analysis codes (neutron transport and thermal hydraulics). 
The geometry generating software must easily interface with the
\gls{DEAP} genetic algorithm driver by accepting Python scripting commands to 
generate 3D geometries. 
The geometry generating software must be compatible with file formats 
accepted by the analysis codes. 
Serpent neutron transport code accepts STL and OpenFOAM file formats. 
The geometry generating software must be easily controlled from the command line
to generate geometries without needing to open a \gls{GUI}, enabling its use 
on a supercomputer. 

\subsubsection{Neutron Transport Code}
Many neutron transport codes have restricted public access. 
In this project, the Serpent Monte Carlo code is used. 
The reasons for choosing Serpent are: 
\begin{itemize}
    \item It is designed to be parallelizable on high performance 
    computers. 
    \item It is already installed on the Blue Waters supercomputer at UIUC. 
    \item UIUC has gained access to the Serpent code through RSICC. 
\end{itemize}

\subsubsection{Thermal Hydraulics Code}

\subsection{Metrics}

\subsubsection{Performance Metrics}
Table \ref{tab:eval-metric} describes the performance metrics that each 
reactor geometry will be evaluated against. 
Based on how `well' each reactor geometry does for each evaluation metric, 
a fitness value is calculated to determine if the reactor geometry is good 
enough to be used to generate the next population of reactor geometries. 

\begin{table}[!htbp]
    \caption{Performance Metrics for each reactor geometry.}
    \label{tab:eval-metric}
    \centering
    \doublespacing
    \small
    \begin{tabular}{ll}
    \hline
    \textbf{Categories} & \textbf{Evaluation Metrics}\\ \hline
    & Maximize power [$\frac{MW}{g}$] \\
    Neutron Transport & \gls{PPF} \\ 
    & keff $\sim$ 1 \\ 
    & Minimize fuel amount [kg] \\ \hline
    Thermal Hydraulics & Maximize surface area for heat transfer [$m^2$]\\ 
    & Minimize pressure drop [Pa]\\ \hline 
    \end{tabular}
\end{table}

Power peaking factor is highest \gls{LPD} divided by average power density in 
the reactor core. 

\subsubsection{Termination Criteria}
The termination criteria is met when all evaluation metrics converge. 
